What to simulate? Inferring the direction for mental rotation

### 2014-02-03 man/cogsci-2014/cogsci-2014.tex
Update manuscript with new analysis

\addtolength{\abovecaptionskip}{-0.25cm}
\addtolength{\belowcaptionskip}{-0.2cm}
\addtolength{\textfloatsep}{-2mm}	% space below "Figure 1: ..."

\input{../../results/D/overall_response_time.tex}
\input{../../results/D/overall_accuracy.tex}
\input{../../results/D/num_chance.tex}
\input{../../results/D/trial_accuracy_corrs.tex}
\input{../../results/D/trial_time_corrs.tex}
\input{../../results/D/response_time_corrs.tex}
\input{../../results/D/accuracy_corrs.tex}

@@

\TODO{need to compute better human vs human correlations}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{../../figures/D/theta_time_corrs.pdf}
    \caption{\textbf{Angle vs. response time}}
    \label{fig:theta-time-corrs}
  \end{subfigure}%
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{../../figures/D/theta_accuracy_corrs.pdf}
    \caption{\textbf{Angle vs. accuracy}}
    \label{fig:theta-accuracy-corrs}
  \end{subfigure}%
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{../../figures/D/human_model_corrs.pdf}
    \caption{\textbf{Human vs. model}}
    \label{fig:human-model-corrs}
  \end{subfigure}
  \vspace{10pt}
  \caption{\textbf{Correlations.} (a) Spearman correlations between
    the minimum angle of rotation and response time. (b) Spearman
    correlations between the minimum angle of rotation and
    accuracy. The \Oc{} and \Th{} models had 100\% accuracy;
    therefore, their correlations are undefined. (c) Pearson
    correlations between human and model, both for response time and
    accuracy. The first set of bars is human vs. human, to give an
    upper bound. All error bars are 95\% confidence intervals.}
\end{figure*}

@@

@@

\TODO{say something about the large step size -- actually produces
  non-intuitive results, even though they are a better fit. with small
  step size (where it doesn't over-rotate) it does even worse!}

>>>>

% space between figure and caption
\addtolength{\abovecaptionskip}{-0.25cm}

% space below "Figure 1: ...", but only for inline figures
\addtolength{\textfloatsep}{-0.5cm}

\input{../../results/D/overall_response_time.tex}
\input{../../results/D/overall_accuracy.tex}
\input{../../results/D/num_chance.tex}
\input{../../results/D/trial_accuracy_corrs.tex}
\input{../../results/D/trial_time_corrs.tex}
\input{../../results/D/response_time_corrs.tex}
\input{../../results/D/accuracy_corrs.tex}
\input{../../results/D/human_corrs.tex}

@@

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{../../figures/D/theta_time_corrs.pdf}
    \caption{\textbf{Angle vs. response time}}
    \label{fig:theta-time-corrs}
  \end{subfigure}%
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{../../figures/D/theta_accuracy_corrs.pdf}
    \caption{\textbf{Angle vs. accuracy}}
    \label{fig:theta-accuracy-corrs}
  \end{subfigure}%
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{../../figures/D/human_model_corrs.pdf}
    \caption{\textbf{Human vs. model}}
    \label{fig:human-model-corrs}
  \end{subfigure}
  \vspace{10pt}
  \caption{\textbf{Correlations.} (a) Spearman correlations between
    the minimum angle of rotation and response time. (b) Spearman
    correlations between the minimum angle of rotation and
    accuracy. The \Oc{} and \Th{} models had 100\% accuracy;
    therefore, their correlations are undefined. (c) Pearson
    correlations between human and model (except the first set of
    bars, which is human vs. human), both for response time and
    accuracy. All error bars are 95\% confidence intervals.}
\end{figure*}

@@

To gauge between-subject reliability, we randomly split subjects into
two groups, computed the average response time and accuracy per
stimulus for each group, and then computed correlations for these two
measures. We repeated this procedure 100 times, and from those samples
computed the median correlations and 95\% confidence intervals. For
response time, the between-subjects correlation was \ExpTimeCorr{},
and for accuracy, it was \ExpAccuracyCorr{} (also shown in
Fig.~\ref{fig:human-model-corrs}).

@@

As noted above, we fit $\sigma_\epsilon=0.6$ for the \Th{} model. This
has the interesting effect of actually causing the \Th{} to
\textit{over}rotate (e.g., the ``flipped'' pair trace in
Fig.~\ref{fig:model-traces}). This is because the step size is large
enough that it sometimes misses the global maximum, and has to do
another full rotation to find it. However, when we use a lower step
size (so that it does not miss the maximum), the fit to human data is
slightly worse.
